A bayesian method of cosine-based word2vec bias

### 2021-06-23 paperDraft/paperDraft.tex

@@

One of the first measures in the discussion has been developed by
Bolukbasi, Chang, Zou, Saligrama, \& Kalai (2016). There, the gender
bias of a word \(w\) is understood as its projection on the gender
direction \(\vec{w} \cdot (\overrightarrow{he} - \overrightarrow{she})\)
(the gender direction is the top principal compontent of ten gender pair
difference vectors). The underlying idea is that no bias is present if
non-explicitly gendered words are in equal distance to both elements in
all explicitly gendered pairs. Given the (ideally) gender netural words
\(N\) and the gender direction \(g\) the direct direct gender bias is
defined as the average distance of the words in \(N\) from \(g\) (\(c\)
is a parameter determining how strict we want to be):

@@

\subsection{The problem with means of
means}\label{the-problem-with-means-of-means}

@@

>>>>

\tableofcontents

@@

\todo{two introductory}

One of the first measures in the discussion has been developed by
Bolukbasi, Chang, Zou, Saligrama, \& Kalai (2016). There, the gender
bias of a word \(w\) is understood as its projection on the gender
direction \(\vec{w} \cdot (\overrightarrow{he} - \overrightarrow{she})\)
(the gender direction is the top principal compontent of ten gender pair
difference vectors). The underlying idea is that no bias is present if
non-explicitly gendered words are in equal distance to both elements in
all explicitly gender pairs. Given the (ideally) gender neutral words
\(N\) and the gender direction \(g\) the direct direct gender bias is
defined as the average distance of the words in \(N\) from \(g\) (\(c\)
is a parameter determining how strict we want to be):

@@

\section{Some methodological
problems}\label{some-methodological-problems}

\section{The problem with means of
means}\label{the-problem-with-means-of-means}

@@

\section{Bayesian estimation}\label{bayesian-estimation}

\begin{itemize}
\item
  reddit i google, ogolnie i z podzialem na protected words
\item
  dokladniej gender, reszta na koniec w zalaczniku
\end{itemize}

\section{Effects of debiasing}\label{effects-of-debiasing}

\section{Discussion}\label{discussion}
